\chapter{Acknowledgements}\markboth{\subsectionfont\itshape\color{activeColor}Acknowledgements}{}
	
	\lettrine[lines=4]{\color{activeColor}F}{irst} of all I would like to thank Anna, who stands by me whatever happens. Without her I would never have had the courage to pursue a PhD.
	Secondly, I would like to thank my parents, who support me in whatever crazy endeavour I throw myself at. 
	I would also like to thank my thesis supervisor, Nadine Halberstadt, who goes beyond the duties and responsibilities as a supervisor. As well as Manuel Barranco, who's pragmatic no-nonsense approach to research I have come to admire and, together with Nadine Halberstadt, made my time as a PhD student fruitful as well as enjoyable.
	And lastly I would like to thank my friends and colleagues for making my time inside- as well as outside the lab a very pleasurable time indeed.
	
	This acknowledgment would not be complete without thanking Nicolas Renon and Emmanuel Courcelle of CALMIP who greatly improved the performance of our code and are always available for a helping hand whenever there are bugs to be crushed.
	
	As well as the Universit\'e F\'ed\'erale Toulouse Midi-Pyr\'en\'ees for financial support through the ``Chaires d'Attractivit\'e 2014'' Programme IMDYNHE.
	
	Last but not least I would like to thank Jérôme Cuny, who, as my parraine de thèse, and my goto representative of the Doctoral School, is always available to help make the administrative side of the PhD go as smoothly as possible.  
	
	This work has been performed under Grants No. FIS2014-52285-C2-1-P from DGI, Spain, and  2014SGR401 from Generalitat de Catalunya.

	The dynamic simulations presented in this work have been carried out thanks to the HPC resources of CALMIP supercomputing center (Grant P1039).

\clearpage{\pagestyle{empty}\cleardoublepage}
